How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-28 docs/PhysicsPaper/StokesErosion.tex
NM

	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.  Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $\mathcal{O}(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.

>>>>

	Our method merges highly-efficient and highly-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies in the Stokes flow regime relevant for groundwater-flow applications~\cite{quaife2018boundary, chiu2020viscous}.  Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated  quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing fluid-flow equations (Stokes) are linear, the nonlinear feedback between evolving microstructure and flow give rise to highly complex and anisotropic configurations.
